\papertitle

### 2014-03-18 final-report/paper.tex
results

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\overview}{Fragment Overview\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions
% explain difference between execution and data skew

@@

\subsubsection{Fragment execution view}
\label{sec:fragment}

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Fig.~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

% Dom

The \overview shows small multiples of the utilization chart as described in the previous section.
Execution skew can be spotted in this view. Furthermore, the user can compare the fragments and find
correlations between the execution of different fragments. This view helps the user navigate to the
right fragment and is not intended to offer further inside into the causes or performance problems.

@@

\subsection{Case 1: Identifying Data Skew using the \network View}

@@

The network visualization at a glance shows how much data was sent between workers. Figure~\ref{fig:network} compares the communication between workers. In Figure~\ref{fig:skew} one can see that most of the data is sent to worker~1 and then worker~5.

>>>>

\newcommand*{\system}{OGEN\xspace}
\newcommand*{\papertitle}{\system: Visualizing Physical Query Execution in a Relational Big Data Management System}
\newcommand*{\graph}{Physical Query Plan\xspace}
\newcommand*{\fragment}{Fragment Execution\xspace}
\newcommand*{\network}{Worker Communication\xspace}
\newcommand*{\overall}{Fragment Overall\xspace}

@@

% What is myria, how does it work (look at report from last quarter but shorter), which query languages are supported
% motivation
% questions (inspiration: https://docs.google.com/a/uw.edu/document/d/1Syn65bu_p6S4RQETaozsleYcRBauQJ7IduYrctS1wrw/edit?pli=1#)
% why is a visualization a good way to answer the questions
% so far the only performance debug mechanism is runtime
% contributions

@@

\subsubsection{Fragment execution view}

@@

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Fig.~\ref{fig:utilization_chart}) shows the utilization
of the cluster over time, inside the selected fragment. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

@@

\subsection{Case 2: Identifying Data Skew using the \network View}

@@

The \network visualization at a glance shows how much data was sent between workers by one query fragment to the next. The two \network views in Figure~\ref{fig:no-skew} and Figure~\ref{fig:skew} were obtained by selecting the Frag0$\rightarrow$Frag2 and Frag1$\rightarrow$Frag2 edges respectively in the \graph view. Figure~\ref{fig:network} displays aggregate data communication between workers. In Figure~\ref{fig:no-skew} the amount of data sent from each worker to every other worker is balanced as opposed to Figure~\ref{fig:skew} where one can see that the volume of data sent to worker~1 and worker~5 outweights data sent to the other workers in the system. This apparent data skew could be caused by partitioning issues.

\subsection{Case 3: Identifying Execution Skew using the \fragment View}
The \fragment visualization allows the user to dive down into query execution schedules at the worker level.
